Source Summaries

### 2020-04-27 paper/sourceSummaries/summary10.tex
source 10

@@

@@

@@

@@

@@

@@

>>>>

\noindent
\subsection{{U}nderstanding and improving security and privacy in multi-user smart homes: a design exploration and in-home user study}

@@

\bibentry{zeng2019understanding}

@@

\noindent
The authors explore user behaviors, needs and possible solutions to multi-user security and privacy issues in generally non-adversarial smart homes. The authors also built a prototype smart home app that includes concrete features like location based access controls, supervisory access controls, and activity notifications. The authors tested their prototype with a month long in-home user study which the authors used to re-evaluate their initial design principles and identified challenges and recommendations for smart home designers and researchers.

@@

\noindent
The authors used Game Theory because they’re testing different smart home models against one another and using feedback of users to find the best model by balancing security with usability.

@@

\noindent
The authors beginning this paper had two research questions: “How should a smart home be designed to address multi user security and privacy challenges (in generally functional households)?” and “What security and privacy behaviors and needs do these smart home users exhibit in practice?”. The authors used initial design principles like access control flexibility, user agency, respect among users, and transparency of smart home behaviors for their smart home model. For access control flexibility the authors allowed users to set up multiple access control schemes like role-based, location-based, supervisory, and reactive access control. For transparency of smart home behaviors the authors had the users be notified of any changes to the house which include the name of the device, the change in state, and the user or process responsible for causing the change. For the user agency the authors used discovery notifications which make clear which devices were nearby and could be used.

@@

\noindent
The authors found in the user study that found misconceptions about their principles. For access control flexibility, the authors found that while it’s important to have different access control models available to the user, having too much complexity in the system can cause users to use the minimum security level. For user agency and respect, the authors found that most of the houses opted to use social norms to support user agency and minimize conflicts instead of access control. For transparency of smart home behaviors, the authors found that they need to look further into the system as users were indifferent to the system. Overall the authors showed how complexity can be a barrier to access control use.

@@

\noindent
How can we improve the usability of smart home access controls? How can we design a smart home model that takes positive household norms into account? What security mechanisms can we introduce into this smart house model for adversarial situations? How can we create a natural language based access control policy creation for smart homes?
